Process Genotypes For Ancestry Analysis

### 2019-09-20 code/Ancestry_PCA.Rmd
Update

```{r libs, include=FALSE}
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)

## Pull 1000Genomes down and process
* Pull out reference populations (CEU, YRI, CHB, JPT)
```{bash pull_1000Genomes, echo=FALSE}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/

CORES=`expr $(nproc) - 2`

@@

#Merge  LDREF Data
for i in {2..22} 
do 
    echo LDREF/1000G.EUR.$i>> MergedChrs.txt
done 
plink --bfile LDREF/1000G.EUR.1 --threads $CORES --merge-list MergedChrs.txt --make-bed --allow-no-sex --out TotalLDRef

#Write SNP List for LDREF Data
plink --threads $CORES --bfile TotalLDRef --write-snplist --out LDREF_SNPs

@@

    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz --snps-only --extract LDREF_SNPs.txt --keep 1000G_IDV.list --threads $CORES --make-bed --out 1000Genomes_chr$i
  rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
done

@@

plink --bfile 1000Genomes_chr1 --merge-list Merge.list --make-bed --out 1000Genomes_Merged

@@

## Process MSBB WGS Data
* Pull VCFs from Synapse
* Convert to plink
* Merge across chromosomes
* Filter for 1000G SNPs
```{bash ProcessMSBB, echo=FALSE}
CORES=`expr $(nproc) - 2`
PATH=$PATH:/home/jgockley/TWAS/bin/
##Pull VCF Files from Synapse
mkdir VCF
synapse get -r syn11707204 --downloadLocation VCF/

@@

#Convert to PLINK
for i in {22..1}
do
  plink --vcf VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i\.recalibrated_variants.MSSM.vcf.gz --threads $CORES --make-bed --allow-no-sex --snps-only --out GWAS_Plink/MSSB_Chr_$i
  rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i\.recalibrated_variants.MSSM.vcf.*
done
rm -r VCF/

@@

CORES=`expr $(nproc) - 2`
PATH=$PATH:/home/jgockley/TWAS/bin/
plink --threads $CORES --bfile GWAS_Plink/MSSB_Chr_1 --merge-list MergedGWAS.txt --extract MSBB_LD_SNPS.txt --make-bed --allow-no-sex --out GWASTotal
#rm -r WGS_Plink/

@@

## Process MAYO Genotyping Data
```{bash MAYO}
CORES=`expr $(nproc) - 2`
#Download
mkdir Mayo
synapse get -r syn8650955 --downloadLocation Mayo/

#Rename Snps with rsIDs & Centimorgan Distance
python BimAnotator.py TotalLDRef.bim Mayo_LDREF_Filt.bim
mv Mayo_LDREF_FiltRenamed.bim Mayo_LDREF_Filt.bim

##Merge Chromsomes in Plink Format 
for i in {2..22} 
do 
    echo GWAS_Plink/MSSB_Chr_$i >> MergedGWAS.txt
done 
plink --threads $CORES --bfile GWAS_Plink/MSSB_Chr_1 --merge-list MergedGWAS.txt --make-bed --allow-no-sex --out GWASTotal
rm -r WGS_Plink/

#Merge  LDREF Data
for i in {2..22} 
do 
    echo LDREF/1000G.EUR.$i>> MergedChrs.txt
done 
plink --bfile LDREF/1000G.EUR.1 --threads $CORES --merge-list MergedChrs.txt --make-bed --allow-no-sex --out TotalLDRef

#Write SNP List for LDREF Data
#plink --threads $CORES --bfile INDV_1000G_Pops --write-snplist --out LDREF_SNPs

#Reformat SNP List for plink filter.txt
awk '{ print $1"\t"$4"\t"$4"\t"$2 }' 1000Genomes_Merged.bim > LDREF_SNPs.txt

##Filter for SNPs in 1000G - LDREF_FiltSNPs
plink --threads $CORES --bfile GWASTotal --extract LDREF_SNPs.txt --make-bed --allow-no-sex --out MSBB_LDREF_FiltSNPs

## ReName the MSBB SNPS so the can be combined
```{python ReNamer}
import sys
import os
import re

@@

>>>>

```{r libs, include=FALSE}
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE,
  results='hide')
```

## Pull 1000Genomes down and process
* Pull out reference populations (CEU, YRI, CHB, JPT)
```{bash pull_1000Genomes, echo=FALSE}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`

@@

#Merge  LDREF Data
for i in {2..22} 
do 
    echo LDREF/1000G.EUR.$i>> MergedChrs.txt
done 
plink --bfile LDREF/1000G.EUR.1 --threads $CORES --silent --merge-list MergedChrs.txt --make-bed --allow-no-sex --out TotalLDRef

#Write SNP List for LDREF Data
plink --threads $CORES --bfile TotalLDRef --silent --write-snplist --out LDREF_SNPs

@@

    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz --snps-only --extract LDREF_SNPs.txt --keep 1000G_IDV.list --silent --threads $CORES --make-bed --out 1000Genomes_chr$i
  rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
done
```

```{bash FOO}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`

@@

plink --bfile 1000Genomes_chr1 --merge-list Merge.list --silent --make-bed --out 1000Genomes_Merged

@@

## Process MSBB WGS Data
* Pull VCFs from Synapse
* Convert to plink
* Merge across chromosomes
* Filter for 1000G SNPs
```{bash ProcessMSBB, echo=FALSE}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`
##Pull VCF Files from Synapse
mkdir VCF
synapse get -r syn11707204 --downloadLocation VCF/

@@

#Convert to PLINK
for i in {22..1}
do
  plink --vcf VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i\.recalibrated_variants.MSSM.vcf.gz --threads $CORES --make-bed --silent --allow-no-sex --snps-only --out GWAS_Plink/MSSB_Chr_$i
  rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i\.recalibrated_variants.MSSM.vcf.*
done
rm -r VCF/

@@

plink --threads $CORES --bfile GWAS_Plink/MSSB_Chr_1 --silent --merge-list MergedGWAS.txt --extract MSBB_LD_SNPS.txt --make-bed --allow-no-sex --out GWASTotal
rm -r WGS_Plink/

@@

### ReName the MSBB SNPS so the can be combined
```{python ReNamer}
import sys
import os
import re

@@

### Finalize the MSBB LD SNP-Set Derived from WGS
```{bash FinalizeMSBB }
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`

#Replace BIM File
mv MSBB_LDREF_FiltSNPsRenamed.bim MSBB_LDREF_FiltSNPs.bim

#Check the SNP-Set
##These numbers should be equal:
grep 'rs' MSBB_LDREF_FiltSNPs.bim | wc -l
wc -l MSBB_LDREF_FiltSNPs.bim

##This Number should be zero:
grep '.' MSBB_LDREF_FiltSNPs.bim | wc -l
```

## Process MAYO Genotyping Data
```{bash MAYO}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`

#Download
mkdir Mayo
synapse get -r syn8650955 --downloadLocation Mayo/

#Rename Snps with rsIDs & Centimorgan Distance
#python BimAnotator.py TotalLDRef.bim Mayo_LDREF_Filt.bim

### ReName the Mayo SNPS so the can be combined
```{python ReNamerMayo}
import sys
import os
import re

InFile = TotalLDRef.bim       #sys.argv[1];
#Gene_Annots/hg19/Merged_hg19_Filt_ENGS.bed
InFileb = Mayo_LDREF_Filt.bim  #sys.argv[2];

### Finalize the Mayo LD SNP-Set Derived from imputed genotyping
```{bash CheckMayo}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`

mv Mayo_LDREF_FiltRenamed.bim Mayo_LDREF_Filt.bim
#Check the SNP-Set
##These numbers should be equal:
grep 'rs' Mayo_LDREF_Filt.bim | wc -l
wc -l Mayo_LDREF_Filt.bim

##This Number should be zero:
grep '.' Mayo_LDREF_Filt.bim | wc -l
```

## Process ROSMAP Genotyping Data
```{bash DosageToHardCalls}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`

#Synapse gets:
declare -A SynArr
arr["1"]=syn5879161
arr["10"]=syn5879677
arr["11"]=syn5879748
arr["12"]=syn5879792
arr["13"]=syn5879812
arr["14"]=syn5879827
arr["15"]=syn5879828
arr["16"]=syn5879830
arr["17"]=syn5879832
arr["18"]=syn5879834
arr["19"]=syn5879835
arr["2"]=syn5879456
arr["20"]=syn5879836
arr["21"]=syn5879837
arr["22"]=syn5879838
arr["3"]=syn5879461
arr["4"]=syn5879463
arr["5"]=syn5879470
arr["6"]=syn5879472
arr["7"]=syn5879473
arr["8"]=syn5879559
arr["9"]=syn5879628

#Pull FAM File
synapse get syn20809809

#Loop Through chromosomes and Process
for i in {1..22}
do

	synapse get ${arr[$i]}

	chr=$i
	echo "1 AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr"$chr".dosage.gz" > b.txt

  #Write a Dosage File
	plink --threads $CORES --fam Updated_Actual_Fam.fam --dosage b.txt list noheader format=1 --write-dosage

  #Convert to plink hard calls 
	plink2 --threads $CORES --fam Updated_Actual_Fam.fam --import-dosage plink.out.dosage format=1 --hard-call-threshold 0.1 --make-bed --out AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr$chr

	rm plink.out.dosage

done
rm b.txt

##Merge Chromsomes in Plink Format 
for i in {2..22} 
do 
    echo AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr$i >> MergedGWAS.txt
done

plink --threads $CORES --bfile AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr1 --silent --merge-list MergedGWAS.txt --extract MSBB_LD_SNPS.txt --make-bed --allow-no-sex --out ROSMAPTotal
rm -r AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr*

#Check the SNP-Set
##These numbers should be equal:
grep 'rs' ROSMAPTotal.bim | wc -l
wc -l ROSMAPTotal.bim

##This Number should be zero:
grep '.' ROSMAPTotal.bim | wc -l
```

##Merge the Genotype Sets and Preform PCA
```{bash MergeAndCall}
